Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events

### 2016-06-23 Manuscript/MS- What is LDD.tex
Edits to section 2 and 3 and Tab 1 SupplMat.

Continuous populations can be modeled with the concepts of isolation by distance and neighborhood size\citep{Wright:1943aa,Wright:1946aa}. The former refers to the case that limited gene dispersal in continuous populations produces demes that are panmictic internally, but are isolated to some extent, from adjacent demes. Each group of reproducing individuals is the neighborhood, defined as the population of a region in a continuum, from which the parents of individuals born near the center may be treated as if drawn at random \citep{Wright:1969mb}. The importance and influence of the dispersal process in determining the size of the neighborhood is given by this equation, which shows how the spatial dispersion (pattern of spatial distribution) of the population influences $N_e$. This influence on the effective size is given by:

\begin{equation}
					N_e= 4 \pi \sigma^2 \delta
\end{equation}

where $\sigma^2$ is the variance of the dispersal distance and $\delta$ is the density of individuals. This formulation is often called the neighborhood size and assumes a normal distribution of distances  between parents and offspring (out in a perfect circular shape from the source). Thus, changes in the variance of dispersal size can affect $N_e$ (highly clumped populations will have reduced $N_e$).

\begin{equation}
					N_b= 4p \sigma^{2d}
\end{equation}

where $d$ is the density of adults per unit area and $\sigma$ is the variance in distance between birth and breeding sites. This is the basic model of ‘Isolation by Distance’ proposed by   \citet{Wright:1943aa,Wright:1946aa}. Under this type of model, migration (gene flow) is given by the variance in dispersal, and not by the proportion of the population that is composed of migrants (denoted $m$), as is the case with island models \citep{Slatkin:1985qb}.

@@

\begin{equation}
  					N_b = 4p (\sigma^2_s + \frac{t \sigma^2_p}{2}) d (1 + t)
\end{equation}

\paragraph*{Empirical Studies of Seed Dispersal}

@@

%------------------------------------------------------------------- Figure 1
\begin{figure}[htbp]
\centerline{\includegraphics[height=25cm]{Fig1.pdf}}
%
%\caption{***}
\end{figure}

\newpage 
%------------------------------------------------------------------- Figure 2
\begin{figure}[htbp]
\centerline{\includegraphics[height=25cm]{Fig2.pdf}}
%
%\caption{***}
\end{figure}

\newpage 
%------------------------------------------------------------------- Figure 3
\begin{figure}[htbp]
\centerline{\includegraphics[height=26cm]{Fig3.pdf}}
%
%\caption{***}
\end{figure}
%----------------------------------------------------------------------------

\newpage 
%------------------------------------------------------------------- Figure 4
\begin{figure}[htbp]
\centerline{\includegraphics[height=27cm]{Fig4.pdf}}
%
%\caption{***}
\end{figure}

>>>>

Continuous populations can be modeled with the concepts of isolation by distance and neighborhood size\citep{Wright:1943aa,Wright:1946aa}. The former refers to the case that limited gene dispersal in continuous populations produces demes that are panmictic internally, but are isolated to some extent from adjacent demes. Each group of reproducing individuals is the neighborhood, defined as the population of a region in a continuum, from which the parents of individuals born near the center may be treated as if drawn at random \citep{Wright:1969mb}. The importance and influence of the dispersal process in determining the size of the neighborhood is given by this equation, which shows how the spatial dispersion (pattern of spatial distribution) of the population influences the effective population size. This influence on the effective size is given by:

\begin{equation}
					N_b= 4 \pi \sigma^2 \delta
\end{equation}

where $\delta$ is the density of adults per unit area and $\sigma$ is the variance in distance between birth and breeding sites. This formulation is often called the neighborhood size and assumes a normal distribution of distances between parents and offspring (out in a perfect circular shape from the source). Thus, changes in the variance of dispersal distance can affect $N_e$ (highly clumped populations will have reduced $N_e$). This is the basic model of "Isolation by Distance" proposed by   \citet{Wright:1943aa,Wright:1946aa}. Under this type of model, migration (gene flow) is given by the variance in dispersal, and not by the proportion of the population that is composed of migrants (denoted $m$), as is the case with island models \citep{Slatkin:1985qb}.

@@

\begin{equation}
  			N_b = 4 \pi (\sigma^2_s + \frac{t \sigma^2_p}{2}) \delta (1 + t)
\end{equation}

where $\sigma^2_s$ is the variance in seed dispersal, $\sigma^2_s$ is the variance in pollen dispersal and $\delta$ is the density of potential parents.

Neighborhood size in plants can be estimated by marking pollen and seeds with fluorescent dyes, tags, or stable isotope enrichment \citep{Carlo:2009wa}. However, these methods do not measure effective pollen or seed movement, but they may be combined with genetic analysis to assess genetic identity and relatedness with hypervariable DNA markers \citep{Levin:1988fm,Nason:1998aa,Godoy:2001} to achieve reliable estimates of both effective population size and neighborhood area.

The extent of neighborhood area in plants can be extremely variable, depending on life-history attributes such as life-span, spacing patterns, mating system, etc. Even a limited sample of available information (Table S1) highlights the fact that the size of neighborhood areas can in some cases exceed the geographic limits of local populations \citep{Nason:1998aa}. The size of neighborhood areas may encompass at least four orders of magnitude, $10{^-2}-10^2$ km in radius, and include many individuals. Therefore, reference to this "genetic/evolutionary" paradigm and reference \citep[sensu][]{Waples:2006ev} may be instrumental to understand the actual role of LDD events in shaping the structuring of genetic pools and contributing to gene dispersal.

Whenever there is a large discrepancy between population area extent and $N_b$ we might expect the frequency of $LDD_{loc}$ and $LDD_{neigh}$ differ enormously. For example, relatively small $N_b$ may rise the importance of $LDD_{loc}$ in preserving scenarios of panmixia within a local population, as most distant dispersal events will disseminate seeds outside the neighborhood of maternal plants.

\subsection*{Empirical analysis of contributions to LDD}

Empirical evaluation of differential contributions to the different forms of LDD events outlined in Table 1 requires identification of source trees as well as assignment of the dispersed propagules to specific vectors or functional groups of vectors \citep{Jordano:2007}. Recently, DNA-barcoding techniques have been developed and successfully applied to the identification of frugivore species contributing to specific seed dispersal events whose source can be identified with genetic, direct assignment techniques \citep{GonzalezVaro:2014ij}. Otherwise, visual identification can reliably assign the genotyped seeds to frugivore species groups based on specific characteristics of scats and regurgitations \citep{Jordano:2007a}.

@@

%------------------------------------------------------------------- Figure 1
\pagestyle{empty}
\begin{figure}[htbp]
\centerline{\includegraphics[height=25cm]{Fig1.pdf}}
%
%\caption{***}
\end{figure}

\newpage 
%------------------------------------------------------------------- Figure 2
\pagestyle{empty}
\begin{figure}[htbp]
\centerline{\includegraphics[height=25cm]{Fig2.pdf}}
%
%\caption{***}
\end{figure}

\newpage 
%------------------------------------------------------------------- Figure 3
\pagestyle{empty}
\begin{figure}[htbp]
\centerline{\includegraphics[height=26cm]{Fig3.pdf}}
%
%\caption{***}
\end{figure}
%----------------------------------------------------------------------------

\newpage 
%------------------------------------------------------------------- Figure 4
\pagestyle{empty}
\begin{figure}[htbp]
\centerline{\includegraphics[height=26cm]{Fig4.pdf}}
%
%\caption{***}
\end{figure}
